---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Comdim package

<!-- badges: start -->
<!-- badges: end -->

ComDim (Common Dimensions) analysis was initially introduced within the context of sensometrics to
analyze conventional and free choice sensory profiling data, and more generally multiblock datasets.
Thereafter, it has gained some popularity in chemometrics and has been extended in different ways to
meet specific needs. Recently, this strategy of analysis has been adapted to the supervised case, under
the name of P-ComDim. Going further, an extension of ComDim to multiblock datasets related to each other by directed relationships has been proposed. In this latter case, 
the datasets at hand are assumed to have a specific pattern of directed relations among them reflecting,
for instance, a chain of influence. The aim of Path-ComDim is to analyze these datasets taking into
account the structural connections among them. 
## Installation

You can install the released version of Comdim from [GitHub](https://github.com) with:

``` r
# install.packages("remotes")
remotes::install_github("vcariou/Comdim")
```

## Example

This is a basic example which shows you how to apply Path-ComDim on a multiblock dataframe:

```{r example}
library(Comdim)
## basic example code
data(RedLosses)
res <- PathComdim(data,Group,delta,20)
```
# How to cite
Luong et al. (2021) International Journal of Food Microbiology
